GPU Efficient Texture Based Bezier Curve Evaluation

### 2015-07-18 Paper/paper.tex
Perf table filled in for machine here at home.

TODO: perf goals are...
* show perf of a few curve types (linear, quadratic, cubic, quartic?), using 1d, 2d, 3d textures.  show based on \# of texture reads (like hw, hwsw, sw).
* show results from laptop as well as work machine. maybe laptop on single GPU?

TODO: perf tests... at 1000x1000
* linear    :  1d texture (1 read vs 2 reads then lerp)
* quadratic :  1d texture (2 reads and lerp vs 3 reads and quadratic bezier), 2d texture (1 read vs 2 reads and lerp vs 3 reads and quadratic Bezier)
* cubic     :  1d texture (3 reads and quad vs 4 reads and quartic bezier), 2d texture (), 3d texture 
* quartic   :  1d texture, 2d texture, 3d texture

TODO: mention that it matters if you are texture lookup bound or not.  correct terms for that = ??

>>>>

The table below was created by running a 1000x1000 pixel shader program where each pixel evaluated a curve using either linear texture sampling (HW or hardware evaluation), or did multiple texture reads to get the control points and then calculated the curve values inside of the shader program (SW or software shader program evaluation).  Actual performance characteristics in real world scenarios will be based on other factors, such as whether the texture is in the texture cache, or whether you are texture fetch bound or compute bound in the shader program.

\begin{tabular}{|l|l l|}
\hline
& \multicolumn{2}{|c|}{NV GF GTX 980m} \\
& \bf{HW} & \bf{SW}\\ \hline
\bf{1D Texture / Linear Curve} & 131.8 $\mu$s & 132.7 $\mu$s \\ \hline
\bf{2D Texture / Quadratic Curve} & 131.1 $\mu$s & 135.1 $\mu$s \\ \hline
\bf{3D Texture / Cubic Curve} & 135.4 $\mu$s & 146.2 $\mu$s \\ \hline
\end{tabular}

TODO: do a test with the cards at work, and put those results here as well!
